Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-10-16 draft.Rmd
Update draft.Rmd

The aim of the article is two-fold. First, we explicitly compare internal and external mobility as a means of improving earnings growth. Second, we compare the relationship between mobility and earnings in two institutional settings, coordinated Germany and the liberal UK (Hall and Soskice, Thelen). Both of the aims stem from wrinkles in the job mobility literature. First, authors rarely see internal promotion as a form of voluntary mobility; instead they tend to focus on the effects of external quits alone. Second, authors exploring the impact of mobility often use single country examples despite the fact that european labour markets are highly divided. Our article highlights this nuance explicitly by comparing quits and promotions in two institutional settings.

Existing theories tell us little about country differences in job mobility. In this section, we focus on two theories specifically. First, in the *job-match* model, found in both economic and sociological approaches, mobility stems from a mismatch between a worker's skills and her rewards or conditions (Jovanvich; Sorensen). Here, countries with low mobility are those able to closely match a worker's skill to a particular job. By the same token, countries with high mobility, are those where job-matching is the worker's responsibility, who may have to take several positions before finding a good "fit" between their skills and their role. Germany is famous for its occupational licensing and its close links between skill producers (educators and tutors) and skill consumers (managers and employers). As a result, workers are better able to match their expectations with their resources quickly. No such relationships exist in the UK, therefore workers must quit and seek promotion often in an effort to secure a "good fit" between their skills and their responsibilities.

By the same token, in the *job-search* model mobility stems from the opportunity of higher wages. Thus, if labour markets have a wide dispersion of wages and wage inequality, workers have more opportunity to match a "reservation wage" to a new position, which leads to higher rates of mobility. As a result, Germany mobility is low because wage inequality and wage dispersion is also low; mobility between positions is less likely to lead to "wage-quits" since differences between positions are minor. In the UK, mobility is high because wage dispersion or wage inequality between positions is also high; in this way a worker has more opportunities to find her "reservation wage".

>>>>

The aim of the article is two-fold. First, we explicitly compare internal and external mobility as a means of improving earnings growth. Second, we compare the relationship between mobility and earnings in two institutional settings, coordinated Germany and the liberal UK (Hall and Soskice, Thelen). Both aims stem from wrinkles in the job mobility literature. First, authors rarely treat internal promotion as a form of voluntary mobility, focusing instead on the effects of external quits alone. Second, authors exploring the impact of mobility often use single country examples despite the fact that European labour markets are divided. Our article highlights the point by comparing quits and promotions in two institutional settings.

Existing theories offer clues as to why countries differ in their rates of job mobility. In this article, we focus on two theoretical works specifically. First, the *job-match* model, found in both economic and sociological approaches, predicts taht mobility stems from a mismatch between a worker's skills and her rewards or conditions (Jovanvich; Sorensen). Here, countries with low mobility are those able to closely match a worker's skill to a particular job. By the same token, countries with high mobility, are those where job-matching is the worker's responsibility, who may have to take several positions before finding a good "fit" between their skills and their role. Germany is famous for its occupational licensing and its close links between skill producers (educators and tutors) and skill consumers (managers and employers). As a result, workers are better able to match their expectations with their resources quickly. No such relationships exist in the UK, where workers are responsibile for matching their skills to their job. Second, in the *job-search* model, mobility stems from the opportunity of higher wages. Thus, if labour markets have a wide dispersion of wages and wage inequality, workers have more opportunities to match a "reservation wage" to a new position, which leads to higher rates of mobility. As a result, Germany mobility is low because wage inequality and wage dispersion is also low; mobility between positions is less likely to lead to "wage-quits" since differences between positions are minor. In the UK, mobility is high because wage dispersion or wage inequality between positions is also high; in this way a worker has more opportunities to find her "reservation wage".
